Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-26 prob.tex
prob.tex "\section{Proof}" Added...
prob.tex "\section{Proof}" Updated...

>>>>

\section{Proof}

Because the importance of Gleason's theorem, its proof have been rewritten
to be more accessible~\cite{CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}.

Here we want to follow \cite{RichmanBridges1999} to prove under suitable
conditions when intervals are more precise, its quantum interval-valued
probability measures are closer to the Born rule. We will focus on
three dimensional Hilbert space, since
